QPLIB: A Library of Quadratic Programming Instances

### 2016-07-29 QPLIB-2.3.tex
added projected gradient on Nick's request

The solvers in Table \ref{t:solvers} which implement incomplete methods are {\sc ConOpt}, {\sc IpOpt}, {\sc Minos}, {\sc SnOpt} and {\sc KNitro}. The former four solvers implement local search algorithms for continuous nonconvex NLPs (a problem class containing QCQ). Note that traditionally {\sc KNitro} used to be a local (nonconvex) NLP solver. All of these solvers implement essentially two types of local search methods for NLP:
%
\begin{itemize}
 \item active set methods ({\sc ConOpt}, {\sc Minos}, {\sc SnOpt});
 %
 \item interior point methods ({\sc IpOpt}, {\sc KNitro}).
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

>>>>

The solvers in Table \ref{t:solvers} which implement incomplete methods are {\sc ConOpt}, {\sc IpOpt}, {\sc Minos}, {\sc SnOpt} and {\sc KNitro}. The former four solvers implement local search algorithms for continuous nonconvex NLPs (a problem class containing QCQ). Note that traditionally {\sc KNitro} used to be a local (nonconvex) NLP solver. All of these solvers implement essentially three types of local search methods for NLP:
%
\begin{itemize}
 \item active set methods ({\sc ConOpt}, {\sc Minos}, {\sc SnOpt}) \cite{Dost09};
 %
 \item interior point methods ({\sc IpOpt}, {\sc KNitro}) \cite{Wright97};
 %
 \item projected gradient methods \cite{CalaMore87:mp, ChenGui13:coap}.
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

\paragraph{Projected gradient methods.}
%
These approaches are similar to active-set methods in that at each iteration they consider the gradient projected onto the set of active constraints, in order to (try to) guarantee feasibility of the next iterate. They differ from active-set methods in that the set of active constraints can change dramatically on each iteration, and they have stronger convergence properties, more akin to those of interior-point methods.
